Near and Mid-infrared properties of known redshift $z\geq5$ Quasars

### 2019-06-14 tex/VHzQ.tex
tables_for_paper/output_table.tex

\title[Infrared properties Very high-$z$ Quasars]
  {Near and Mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
%\author[N. Ross, N. Cross \& C. Ross]
{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross \\ 
%{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk}, Nicholas J. G. Cross and Christine B. Ross \\ 
Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\ }

@@

For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.  For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.  Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}. The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.

@@

Table~\ref{tab:output_table} represents the culmination of this
effort, and we now exam the assembly of its contents in more detail.
\begin{landscape}
      \input{../tables_for_paper/output_table}
\end{landscape}

@@

We thank:
\begin{list}{$\circ$}{}  
\item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
\end{list}

>>>>

\title[Infrared properties Very high-$z$ Quasars]
  {Near and Mid-infrared properties of known redshift $z\geq5$ Quasars}
\author[Ross \& Cross]
%\author[N. Ross, N. Cross \& C. Ross]
{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross \\ 
%{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk}, Nicholas J. G. Cross and Christine B. Ross \\ 
Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\ }

@@

For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.  For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.  Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}. The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius. Critically, we also note that

@@

Table~\ref{tab:output_table} represents the culmination of this
effort, and we now exam the assembly of its contents in more detail.

\begin{landscape}
      \input{../tables_for_paper/output_table}
\end{landscape}

@@

We thank:
\begin{list}{$\circ$}{}  
\item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
 \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
\end{list}
